Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-04-12 participants.tex

In our experience, a participant group that is diverse across categories of diversity, gender, discipline and career track helps to ensure we meet these objectives.
To achieve this diversity, we advocate for a selection process that is as quantitative and transparent as possible, enabling participants to hold organizers accountable for their selection decisions.

>>>>

In our experience, a participant group that is diverse across categories of minority status, geographical origin, gender, discipline and career track helps to ensure we meet these objectives.
To achieve this diversity, we advocate for a selection process that is as quantitative and transparent as possible, enabling participants to hold organizers accountable for their selection decisions.

Participant selection is an intrinsically difficult process that is fraught with personal and structural biases~\cite[e.g.][]{sunstein2015wiser}. Traditional selection processes rely heavily on internal heuristics of reviewers, including using unrelated characteristics including name~\cite{bertrand2004} or gender~\cite{mossracusin2012} as a cipher for suitability. On the other hand, while purely mechanistic procedures may to be able to mitigate some reviewer biases, this may come at a cost of baking in structural inequalities. A blind selection purely on merit may be flawed if some groups of applicants have been systematically disadvantaged in certain ways: for example,
